


%__________   DEDICATION  ______________________________
\vspace*{2in}
\begin{center}
	\emph{To all Ukrainian soldiers, volunteers, and those who tirelessly contribute to Ukraine’s resilience and victory.}
\end{center}
%____________________________________________________________

\newpage


%__________   ACKNOWLEDGMENTS  ______________________________
\vspace*{0.5in}
\begin{center}
	\section*{ACKNOWLEDGMENTS}
\end{center}
%\addcontentsline{toc}{section}{ACKNOWLEDGMENTS}


\noindent

I would like to sincerely thank my supervisor, Prof. Sudhir Malik, for his continued support, thoughtful guidance, and encouragement throughout my studies. I’m especially grateful for the opportunities provided to stay engaged with the CMS community and contribute meaningfully to its research efforts. His insight into the broader context of the field has been especially valuable.

This work would not have been possible without the guidance of Prof. Corrinne Mills (UIC) and Dr. Gabrielle Benelli (FNAL), whose support during the Guest and Visitor (G/&V) program at Fermilab was especially crucial. Their combined expertise and feedback helped shape many aspects of this work, both during the program and beyond. I am also thankful to the FNAL Testbeam group and the LPC staff at Fermilab for their collaboration and continued support throughout this effort.

I am grateful to the faculty and staff of the Physics Department at the University of Puerto Rico at Mayagüez for their support throughout my time at the university. In particular, I would like to thank Prof. Pablo Marrero and Prof. Samuel Santana for serving on my committee, as well as Prof. Rafael Ramos for his guidance.

Finally, I wish to thank my family and closest people for their unwavering support, patience, and understanding. I also want to express my heartfelt gratitude to the Ukrainian soldiers and all those working toward Ukraine’s victory. Their courage and resilience safeguard my home and allow me to continue my work with the hope of one day witnessing a free and enduring Ukraine prevail.
